A fast algorithm for computing best response behaviour strategies in two-person sequential games

### 2014-07-25 paper.tex
more

\section{Introduction}
\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{sboyd}) on convex optimization for a tutorial introduction to these notions. Viz,\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$\mathbb{R}_+$: \quad \textit{nonnegative part of the real-line $\mathbb{R}$}\\
$i_C$: \quad \textit{indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{euclidean projector onto the convex set $C$}\\
$(x)_+$: \quad \textit{component-wise maximum of the vector $x$ and 0}\\
$\|K\|$: \quad \textit{operator norm of the matrix $K$}\\
$F^*$: \quad \textit{Fenchel transform of the convex l.s.c function $F$}\\
$E^{-1}(U)$: \quad \textit{pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

\begin{equation}
  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
\end{equation}

In section II, we give a brief overview of existing methods for solving (1). We elaborate our proposed algorithm in section III.

@@

\section{The proposed algorithm}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving (1).

@@

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^q}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
\end{equation}
where:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (i_{\{y_0\}} - \zeta^Te)
  \end{aligned}
  \right\}
\end{equation}

Furthermore, $F^*$ and $G$ have resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}
This way, we obtain following primal-dual algorithm for solving (2).

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y$}%%  \textbf{Let}
\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$; $k = 0$.\\
\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
\Repeat{
  convergence}{
  \begin{eqnarray*}
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma (e - E\tilde{x}^{(k)})\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
\label{Tab:pseudocode_lbfgs}
\end{algorithm}

@@

%\begin{remark}
%% Due to the independence of $(1 + \sigma \partial F^*)^{-1}$ on $\sigma$, we can always choose the pair
%% $(\tau, \sigma)$ , such that $\tau\sigma \|\tilde{\nabla}\|^2 \le 1$ and $\tau \rho(X^TX) \le \alpha$.
% \end{remark}
%% We note that if the pair $(\tau, \sigma)$ is chosen such that $\tau \rho(X^TX) < \alpha$,
%% then (6) can be approximated by
%% \begin{equation}
%% (1 + \tau \partial G)^{-1}(w) \approx (1 - \frac{\tau}{\alpha}X^TX)(w - \frac{\tau}{\alpha} X^Ty)
%% \end{equation}

%% Prediction of external variates from brain images has seen an
%% explosion of interest in the past decade, in cognitive neurosciences
%% to predict cognitive content from functional imaging data such as fMRI
%% \cite{haxby2001,kamitani2005,haynes2006} or for medical diagnosis
%% purposes \cite{fan2008}. Given that brain images are
%% high-dimensional objects --composed of many voxels-- and the
%% number of samples is limited by the cost of acquisition, the
%% estimation of a multivariate predictive model is ill-posed and calls
%% for regularization. This regularization is central as it encodes the
%% practicioner's priors on the spatial maps. For brain mapping, it has
%% been shown that regularization schemes based on sparsity (Lasso or
%% $\ell_1$ family of models) \cite{carroll2009} or Total Variation (TV),
%% that promotes spatial contiguity \cite{michel2011}, perform well for
%% prediction. The combination of these, hereafter dubbed
%% ``TV$-\ell_{1}$'', extracts spatially-informed %% --and thus, more
%% %% interpretable-- 
%% brain maps that are more stable \cite{baldassarre2012}
%% and recover better the predictive regions
%% \cite{gramfort-etal:2013a}. In addition, this prior leads to
%% state-of-the-art methods for extraction of brain atlases
%% \cite{abraham2013}.

%% However, the corresponding optimization problem is
%% intrinsically hard to solve. The reason for this is two-fold. First and
%% foremost, in fMRI studies, the design matrix $\mathbf{X}$ is ``fat''
%% ($n \ll p$), dense, ill-conditioned with little algebraic structure to be
%% exploited, making the optimization problem ill-conditioned. Second, the
%% penalty is not smooth, and while the $\ell_{1}$ term is \emph{proximable}
%% (via \emph{soft-thresholding}), the TV term does not admit a closed-form proximal
%% operator. Thus neither gradient-based methods (like Newton, BFGS, etc.) nor proximal methods (like
%% ISTA~\cite{daubechies2004}, FISTA~\cite{beck2009a}) can be used in the
%% traditional way.

%% While the quality of the optimization may sound as a minor
%% technical problem to the practitioner, the sharpening effect of TV and the
%% sparsity-inducing effect of $\ell_1$ come into play only for
%% well-optimized solutions. As a result, the brain maps extracted vary
%% significantly as a function of the tolerance on the solver (see
%% Fig.\,\ref{fig:maps_tolerance}).

%% \begin{figure*}
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_1.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-1}$}}\hspace*{.315\linewidth}}\hfill%
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_0_001.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-3}$}}\hspace*{.315\linewidth}}\hfill%
%% \includegraphics[width=.32\linewidth]{maps/face_vs_house_tol_1e-05.pdf}%
%% \llap{\color{white}\raisebox{.17\linewidth}{\rlap{\sffamily Stopping:
%%       $\Delta E < 10^{-5}$}}\hspace*{.315\linewidth}}%

%% \caption{TV$-\ell_1$ maps for the face-house discrimination task on
%%   the visual recognition dataset, with regularization parameters chosen by
%%   cross-validation, for different stopping criteria.
%%   Note that
%%   the stopping criterion is defined as a threshold on the energy
%%   decrease per one iteration of the algorithm, and thus differs from
%%   the tolerance displayed in figure \ref{Fig:MSEtimes}.  This figure shows
%%   the importance of convergence for problem \eqref{eq:opt_pb}, and motivates
%%   the need for a fast solver.}%
%% \label{fig:maps_tolerance}
%% \end{figure*}

%% In this contribution, we compare a comprehensive list of
%% solvers, all implemented with great care, for solving TV$-\ell_1$
%% regression with a focus on convergence time. First we state the formal
%% problem solved.
%% In section \ref{sec:algos}
%% we present the various algorithms. Experiments done and the results obtained are presented in secions
%%  \ref{sec:experiments} and \ref{sec:results}
%% respectively. Section \ref{sec:discusion} concludes the paper with
%% general recommendations.

%% \section{Formal problem statement and notations}

%% \label{sec:problem_statement}

%% We denote by $\mathbf{y} \in \mathbb{R}^{n}$ the targets to
%% be predicted, and $\mathbf{X}\in\mathbb{R}^{n \times p}$ the
%% brain images related to the presentation of different
%% stimuli. $p$ is the number of voxels and $n$ the number of
%% samples (images). Typically, $p \sim 10^3-10^5$ (for a whole volume),
%% while $n \sim 10-10^3$.  Let $\Omega \subset \mathbb{R}^3$ be
%% the 3D image domain, discretized on a finite grid. The coefficients
%% $\mathbf{w}$ define a spatial map in $\mathbb{R}^p$. Its gradient at a
%% voxel $\omega \in \Omega $ reads:
%% \begin{eqnarray}
%%   \mathbf{\nabla} \mathbf{w}(\omega) := [\nabla_{x} \mathbf{w}(\omega),
%%     \nabla_{y} \mathbf{w}(\omega), \nabla_{z} \mathbf{w}(\omega)] \in
%%   \mathbb{R}^3,
%% \end{eqnarray}
%% where $\nabla_{u}$ is the spatial difference operator along
%% the $u$-axis. Thus $\mathbf{\nabla}$
%% is a linear operator $\in \mathbb{R}^{3p \times
%%   p}$ with adjoint $\mathbf{\nabla} ^T = -\dive \in \mathbb{R}^{p
%%   \times 3p}$. $\Delta := \nabla ^T \nabla \in
%% \mathbb{R}^{p \times p}$ is the Laplace operator.

%% TV$-\ell_1$ regression leads to the following non-smooth convex
%% optimization problem \cite{gramfort-etal:2013a}:
%% \begin{eqnarray}
%%   \mathbf{\hat{w}} := \argmin_{\mathbf{w}}\;\{E(\mathbf{w}) :=
%%   \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
%%   J(\mathbf{w})\},
%%   \label{eq:opt_pb}
%% \end{eqnarray}
%% where $J(\mathbf{w}) := \zeta\|\mathbf{w}\|_{\ell_{1}} + (1 -
%% \zeta)\|\mathbf{w}\|_{TV}$ is the regularization and $\alpha \ge 0$
%% controls the amount of regularization. The
%% parameter $\zeta \in [0, 1]$, also known as the $\ell_{1}$ \textit{ratio}, is the trade-off between the
%% sparsity-inducing penalty $\ell_{1}$ (Lasso) and TV (isotropic Total
%% Variation):
%% % also known as the $\ell_{1}$\emph{-ratio},
%% % XXX = $\ell_{1}$\emph{-ratio} is sklearn jargon
%% \begin{eqnarray}
%% \|\mathbf{w}\|_{\ell_{1}} := \sum_{\omega \in
%%   \Omega}|\mathbf{w}(\omega)|;\;\;\textbf{ }\|\mathbf{w}\|_{TV} :=
%% \sum_{\omega \in \Omega} \|\nabla \mathbf{w}(\omega)\|_{2} \enspace .
%% %% \\
%% %% &=& \sum_{\omega \in
%% %% \Omega}
%% %% \sqrt{\nabla_{x} \mathbf{w}(\omega)^2 + \nabla_{y} \mathbf{w}(\omega)^2 +
%% %%   \nabla_{z}\mathbf{w}(\omega)^2}\\
%% \end{eqnarray}
%% $\mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w})$
%% is the loss function. Here, we focus on the squared loss
%% and the logistic loss, defined \emph{e.g.} in \cite{michel2011}. The
%% squared loss is natural for regression settings, where $\mathbf{y}$ is a
%% continuous variable, but it may also be used for classification
%% \cite{suykens2002}. The logistic loss is harder to optimize, but
%% more natural for classification settings.

%% \section{Algorithms}
%% \label{sec:algos}

%% In this section, we present the algorithms we benchmarked for solving
%% problem \eqref{eq:opt_pb}.

%% \paragraph{ISTA/FISTA}
%% ISTA~\cite{daubechies2004}, and its accelerated variant
%% FISTA~\cite{beck2009a}, are proximal gradient approaches: the go-to
%% methods for non-smooth optimization. In their seminal introduction of TV
%% for fMRI, Michel \emph{et al.} \cite{michel2011} relied on ISTA.
%% The challenge of these methods for TV is that the proximal operator
%% %% \footnote{The proximal operator (or prox for short) can be seen as a generalization of projection unto convex set.}
%%   of TV
%% cannot be computed exactly; we approximate it in an inner FISTA loop
%% \cite{beck2009b,michel2011}.
%% % , \cite{gramfort-etal:2013a}.
%% %%  and must itself be solved by a
%% %% FISTA\footnote{Note that solving TV and TV$-\ell_1$ are formally very
%% %% close \cite{gramfort-etal:2013a}.
%% % }
%% % \cite{beck2009b,michel2011}. 
%% Here, for all FISTA implementations we use
%% the faster monotonous FISTA variant \cite{beck2009b}. We control the
%% optimality of the TV proximal via its dual gap \cite{michel2011} and
%% use a line-search strategy in the monotonous FISTA to decrease the
%% tolerance as the algorithm progresses, ensuring convergence of the
%% TV-$\ell_1$ regression with good accuracy.

%% \paragraph{ISTA/FISTA with backtracking}
%% A key ingredient in FISTA's convergence is the Lipschitz
%% constant $L(\mathcal{L})$, of the derivative of smooth part of the objective function
%% . The tighter the upper bound used for this constant,
%% the faster the resulting FISTA algorithm. In FISTA, the main use of 
%% $L(\mathcal{L})$ is the fact that: for any
%% stepsize $0 < t \le 1/L(\mathcal{L})$ and for any point $\mathbf{z}$,
%% \begin{equation}%
%%   \begin{gathered}
%%     \mathcal{L}(\mathbf{p}_{t}(\mathbf{z})) \le
%%     \mathcal{L}(\mathbf{z}) + \mathbf{r}_{t}^T\nabla
%%     \mathcal{L}(\mathbf{z}) + \frac{1}{2t} \|\mathbf{r}_{t}\|_{2}^2,
%%     \text{  where} \quad\\
%%     \mathbf{p}_{t}(\mathbf{z}) := \textrm{prox}_{\alpha t J}(\mathbf{z} - t
%%     \nabla \mathcal{L}(\mathbf{z})) \,\text{  and  }\,
%%     \mathbf{r}_{t} :=
%%     \mathbf{p}_{t}(\mathbf{z}) - \mathbf{z} \quad
%%   \end{gathered}
%%   \label{eq:fista_ineq}
%% \end{equation}
%% In least-squares regression, $L(\mathcal{L})$ is precisely the largest
%% singular value of the design matrix $\mathbf{X}$.
%% For logistic
%% regression however, the tightest known upper bound for
%% $L(\mathcal{L})$ is $\|\mathbf{X}\|\|\mathbf{X}^T\|$ (for example see Appendix A of
%% \cite{yuan2012}), which performs
%% very poorly locally (i.e, stepsizes $\sim 1 / L(\mathcal{L})$ are
%% sub-optimal locally). A way to circumvent this difficulty is
%% \emph{backtracking line search} \cite{beck2009a}, where one tunes the
%% stepsize $t$ to satisfy inequality \eqref{eq:fista_ineq} locally at
%% point $\mathbf{z}$.

%% \paragraph{ADMM: Alternating Direction Method of Multipliers}
%% ADMM is a Bregman Operator Splitting primal-dual method for
%% solving convex-optimization problems by splitting the
%% objective function in two convex terms which are functions of linearly-related auxiliary variables
%% \cite{boyd2010}.  ADMM is particularly appealing for problems such as TV
%% regression: using the variable split $\mathbf{z}
%% \leftarrow \nabla \mathbf{w}$, the regularization is a simple $\ell_{1}/\ell_2$
%% norm on $\mathbf{z}$ for which the proximal is exact and computationally
%% cheap. However, in our settings, limitations of ADMM are:
%% \begin{itemize}
%% \item the $\mathbf{w}$-update involves the inversion of a large ($p \times p$)
%%   ill-conditioned linear operator (precisely a weighted sum of
%%   $\mathbf{X}^T\mathbf{X}$, the laplacian $\Delta$, and the identity
%%   operator).
%% \item the $\rho$ parameter for penalizing the split
%%   residual $\mathbf{z} - \nabla \mathbf{w}$ is hard to set (this is still an
%%   open problem), and though under mild conditions ADMM
%%   converges for any value of $\rho$, the convergence rate depends
%%   on $\rho$.
%% \end{itemize}

%% \paragraph{Primal-Dual algorithm of Chambolle and Pock \cite{chambolle2010}}
%% this scheme is another method based on operator splitting.
%% Used for fMRI TV regression by \cite{gramfort-etal:2013a},
%% it does not require setting a hyperparameter.  % XXX : this is wrong you have the tau / sigma
%% However it is a first-order single-step method and is thus more impacted by the
%% conditioning of the problem. Note that here we explore this primal-dual
%% method only in the squared loss setting, in which the algorithm can be accelerated by
%% precomputing the SVD of $\mathbf{X}$ \cite{gramfort-etal:2013a}
%% .

%% \paragraph{HANSO \cite{lewis2008}}
%% a modified LBFGS scheme based on gradient 
%% sampling methods \cite{burke2005} and inexact
%% line-search. For non-smooth problems as in our case, the algorithm relies on
%% random initialization, to avoid singularities with high probability. 
%% Here, we used the original authors' implementation.

%% \paragraph{Uniform approximation by smooth convex surrogates}
%% $\ell_{1}$ (resp. TV) is differentiable almost everywhere,
%% with gradient $\bigl(\textbf{w}(\omega)/|\textbf{w}(\omega|))_{\omega
%%   \in \Omega}$ (resp. $-\dive (\nabla \mathbf{w}/\|\nabla
%% \mathbf{w}\|_2)$), except at voxels $\omega$ of the weights map where
%% \textbf{w}$(\omega) = 0$ (resp. $\|\nabla \mathbf{w}(\omega)\|_{2} =
%% 0$), corresponding to black spots (resp. edges).  A convenient
%% approach (see for example \cite{NESTA, nesterov2005a, nesterov2005b,
%%   beck2012}) for dealing with such singularities is to uniformly
%% approximate the offending function with smooth surrogates that
%% preserve its convexity. Given  % I removed "and other important properties"
%% a smoothing parameter $\mu > 0$, we define \emph{smoothed} versions
%% of $\ell_1$ and TV:
%% %
%% \begin{eqnarray}
%%   \left.
%%   \begin{aligned}
%%     \|\mathbf{w}\|_{\ell_{1},\mu} &:= \sum_{\omega \in \Omega}
%%     \sqrt{\mathbf{w}(\omega)^2 + \mu^2} \quad\\
%%     \|\mathbf{w}\|_{TV, \mu} &:=
%%     \sum_{\omega \in \Omega} \sqrt{\|\nabla \mathbf{w}(\omega)\|_{2}^2 +
%%     \mu^2} \quad
%%     \end{aligned}
%%     \right\}
%% \end{eqnarray}
%% These surrogate upper-bounds are convex and everywhere-differentiable
%% with gradients that are Lipschitz-continuous with constants $1/\mu$ and
%% $\|\nabla\|^2(1/\mu) = 12 / \mu$ respectively.
%% %
%% They lead to smoothed versions of problem \eqref{eq:opt_pb}:
%% \begin{align}
%%   \mathbf{\hat{w}}_{\mu} := \argmin_{\mathbf{w}}\;
%%   \{E_{\mu}(\mathbf{w}) := \mathcal{L}(\mathbf{y}, \mathbf{X}, \mathbf{w}) + \alpha
%%     J_{\mu}(\mathbf{w})\},
%%   \label{eq:sopt_pb}
%% \\
%%     \text{where} \quad
%%     J_{\mu}(\mathbf{w}) :=\zeta \|\mathbf{w}\|_{\ell_{1},\mu} +
%%     (1 - \zeta)\|\mathbf{w}\|_{TV, \mu} \quad
%% \end{align}

%% To solve \eqref{eq:opt_pb}, we consider problems of the form
%% \eqref{eq:sopt_pb} with $\mu \rightarrow 0^+$: we start with a coarse
%% $\mu$ ($= 10^{-2}$, \emph{e.g}) and cheaply solve the $\mu$-smoothed problem
%% \eqref{eq:sopt_pb} to a precision $\sim \mu$ using a fast
%% iterative oracle like the LBFGS \cite{ciyou1994}; we
%% obtain a better estimate for the solution; then we decrease $\mu$ by a fixed factor,
%% and restart the solver on problem \eqref{eq:sopt_pb} with this solution; and so on, in a 
%% \emph{continuation} process~\cite{NESTA} detailed in Alg.
%% \ref{Tab:pseudocode_lbfgs}.

%% \begin{algorithm}[htb]
%% \caption{LBFGS algorithm with continuation} \textbf{Let}
%% $\epsilon > 0$ be the desired precision, $\beta$ ($0 < \beta <
%% 1$) be the rate of decay of the smoothing parameter $\mu$, and $\gamma > 0$ be a constant.  Finally,
%% let LBFGS: $(E_\mu, \mathbf{w}^{(0)}, \epsilon) \mapsto \mathbf{w}$ be
%% an oracle which when warm-started with an initial guess
%% $\mathbf{w}^{(0)}$, returns an $\epsilon$-optimal
%% solution (i.e $E_\mu(\mathbf{w}) - E_\mu^{*} < \epsilon$) for problem \eqref{eq:sopt_pb}.\\
%% \textbf{Initialize} $ 0 < \mu^{(0)}$ ($= 10^{-2}$, \emph{e.g}),
%% $\mathbf{w}^{(0)}\in \mathbb{R}^p$, and $k = 0$.\\
%% \Repeat{$\gamma\mu^{(k)}
%%   < \epsilon$}{
%%   \begin{eqnarray*}
%%     \mathbf{w}^{(k + 1)} &\leftarrow& \mbox{LBFGS}(E_{\mu^{(k)}},
%%     \mathbf{w}^{(k)}, \gamma\mu^{(k)})\\
%%     \mu^{(k + 1)} &\leftarrow& \beta \mu^{(k)} \\
%%     k &\leftarrow& k + 1
%%   \end{eqnarray*}
%% } \Return $\mathbf{w}^{(k)}$
%% \label{Tab:pseudocode_lbfgs}
%% \end{algorithm}

%% This algorithm is not faster than
%% $\mathcal{O}(1/\epsilon)$: indeed a good optimization algorithm
%% for the sub-problem \eqref{eq:sopt_pb} is $\mathcal{O}(\sqrt{L_{\mu}/\epsilon})$
%% \cite{nesterov1983}, and $L_{\mu} \sim 1 / \mu \sim 1 / \epsilon$. We
%% believe that this bound is tight but a detailed analysis is
%% beyond the scope of this paper.

%% \section{Experiments on fMRI datasets}
%% \label{sec:experiments}
%% We now detail experiments done on publicly available
%% data. All experiments were run full-brain without spatial smoothing.

%% \paragraph{Visual recognition}
%% \label{subsec:haxby}
%% Our first benchmark dataset is a popular block-design fMRI dataset from a study on face and
%% object representation in human ventral temporal cortex  \cite{haxby2001}.
%% It consists of
%% 6 subjects with 12 runs per subject. In each run, the subjects
%% passively viewed images of eight object categories, grouped
%% in 24-second blocks separated by intermittent rest periods. This
%% experiment is a classification task: predicting the object category. We use a
%% two-class prediction target: $\mathbf{y}$ encodes faces versus houses.
%% The design matrix $\mathbf{X}$ is made of
%% time-series from the full-brain mask of $p = 23\,707$ voxels over $n =
%% 216$ TRs, of a single subject (subj1).

%% \paragraph{Mixed Gambles}
%% Our second benchmark dataset is a study in which
%% subjects were presented with mixed (gain/loss) gambles, and decided
%% whether they would accept each gamble \cite{mixedgambles2007}.  No outcomes of these gambles
%% were presented during scanning, but after the scan three gambles were
%% selected at random and played for real money. The prediction task here is
%% to predict the magnitude of the gain and thus a regression on a
%% continuous variable \cite{jimura2012}. The data is pooled across
%% subjects, resulting in 768 samples, each an image of 33\,177 voxels.

%% % We validate our algorithms on both simulated and real data.
%% \smallskip

%% We study the convergence of the algorithms for parameters close to the
%% optimal parameters set by 10-fold cross-validation to maximize prediction
%% accuracy.

%% \begin{figure*}
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_lr_11th.json .9 --pdb
%% \hspace*{-.01\linewidth}%
%% \includegraphics[width=.6\linewidth]{bench/haxby_lr_energy.pdf}
%% \hspace*{-.09\linewidth}%
%% \includegraphics[width=.6\linewidth]{bench/haxby_lr.pdf}%
%% % \vspace{-2ex}
%% \caption{TV$-\ell_1$ penalized Logistic Regression on the visual
%% recognition face-house
%%   discrimination task. \textbf{Left}: excess energy $E(\mathbf{w}_t) -
%% E(\mathbf{w}_{t})_{t \rightarrow \infty}$ as a function 
%% of time.
%% \textbf{Right}: convergence time of the various solvers for different
%% choice of regularization parameters.
%% Broken lines correspond to a tolerance of $10^{0}$,
%%   whilst full-lines correspond to $10^{-2}$.  The thick vertical line
%% indicates the best model selected by cross-validation.}
%% \label{Fig:HaxbyLR}
%% \end{figure*}

%% %% \paragraph{Haxby 2001: TV$-\ell_{1}$ penalized Least-Squares Regression}
%% %% See figure \ref{Fig:HaxbyMSE}
%% \begin{figure*}
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/haxby_mse_10th.json 1e-2 --pdb
%% \includegraphics[width=.6\linewidth]{bench/haxby_mse.pdf}%
%% \hspace{-.09\linewidth}%
%% % generate with: ipython ../wip/tv_l1_solver/plot_parallel_plots.py bench/poldrack_mse_12th.json 2e1 --pdb
%% \includegraphics[width=.6\linewidth]{bench/poldrack_mse.pdf}
%% % \vspace{-2ex}
%% \caption{TV$-\ell_1$ penalized Least-Squares Regression. \textbf{Left}:
%%   on the visual recognition  face-house discrimination task; \textbf{Right}: on the
%%   Mixed gambles dataset. Broken lines correspond to a tolerance of $10^{0}$,
%%   whilst full-lines correspond to $10^{-2}$. The thick vertical line
%% indicates the best model selected by cross-validation.}
%% \label{Fig:MSEtimes}
%% \end{figure*}

%% \section{Results: convergence times}
%% \label{sec:results}
%% Here, we present benchmark results for our experiments. Figure
%% \ref{Fig:HaxbyLR} gives results for the logistic regression run on the
%% visual recognition dataset: convergence plots of energy as a function of
%% time show that all methods are asymptotically decreasing. Figure
%% \ref{Fig:HaxbyLR} left, shows the time required to give a convergence
%% threshold, defined as a given excess energy compared to the lowest energy
%% achieved by all methods, for different choices of regularization
%% parameters. Similarly, figure \ref{Fig:MSEtimes} shows convergence times
%% for squared loss on both datasets. For these figures,
%% each solver was run for a maximum of 1 hour per problem. Solvers that do
%% not appear on a plot did not converge for the corresponding
%% tolerance and time budget.

%% For logistic loss, the most serious contender is
%% algorithm \ref{Tab:pseudocode_lbfgs}, LBFGS applied on a smooth
%% surrogate, followed by ADMM, however ADMM performance
%% varies markedly depending on the choice of $\rho$. For the squared loss
%% FISTA and algorithm \ref{Tab:pseudocode_lbfgs} are the best performers,
%% with FISTA achieving a clear lead for the larger mixed-gambles dataset.
%% Note that in the case of strong regularization the problem is better
%% conditioned, and first-order methods such as the
%% primal-dual approach can perform well.

%% %% \paragraph{Haxby: TV$-\ell_{1}$ penalized Logistic Regression}
%% %% TV$-\ell_{1}$ penalized Logistic Regression...See figure \ref{Fig:HaxbyLR}

%% \section{Conclusions: approaches to prefer}
%% \label{sec:discusion}

%% TV$-\ell_{1}$ penalized regression for brain imaging leads to
%% very high-dimensional, non-smooth and very ill-conditioned optimization
%% problems. We have presented a comprehensive comparison of state-of-the-art
%% solvers in these setting. Solvers were implemented with all known
%% algorithmic improvements and implementation were carefully profiled and
%% optimized.

%% Our results outline best strategies: monotonous FISTA with a adaptive
%% control of the tolerance of the TV proximal operator, in the case of
%% squared loss; smoothed quasi-newton based on surrogate upper-bounds of
%% the non-smooth norms for logistic loss. While these algorithms are
%% variants of existing approaches, we present here novel additions useful
%% for the TV or TV$-\ell_1$ settings. The fact that the smooth approaches emerge
%% as fast solvers on these non-smooth problems is not unexpected as
%% \emph{i)} the amount of regularization is small \emph{ii)} the prevailing
%% term is smooth and very ill conditioned, thus calling for second-order
%% methods such as Newton or quasi-Newton.

%% For neuroimaging applications, our study has highlighted the need to
%% converge to a good tolerance and the corresponding difficulties. Lack of
%% good solver and explicit control of tolerance can lead to brain maps and
%% conclusions that reflect properties of the solver more than of the
%% TV$-\ell_1$ solution.

%% %\section{Acknowledgements}
%% %% \label{subsec:acknowledgements}
%% %This work was supported by the  Human Brain Project.

%% \medskip \noindent
%% \textbf{Acknowledgments:}
%% This work was supported by the  Human Brain Project.

%% % ==========
%% % = biblio =
%% % ==========
%% % {\small
%% \bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
\end{document}

>>>>

\section{Introduction}
\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$\mathbb{R}_+$: \quad \textit{nonnegative part of the real-line $\mathbb{R}$}\\
$i_C$: \quad \textit{indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{euclidean projector onto the convex set $C$}\\
$(x)_+$: \quad \textit{component-wise maximum of the vector $x$ and 0}\\
$\|K\|$: \quad \textit{operator norm of the matrix $K$}\\
$F^*$: \quad \textit{Fenchel transform of the convex l.s.c function $F$}\\
$E^{-1}(U)$: \quad \textit{pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

\begin{equation}
  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
  \label{eq:opt_pb}
\end{equation}

In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}. We elaborate our proposed algorithm in section III.

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithmic 1 of \cite{chambolle2010}.

@@

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^q}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
  \label{eq:pd_opt}
\end{equation}
where:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (i_{\{y_0\}} - \zeta^Te)
  \end{aligned}
  \right\}
\end{equation}

Furthermore, $F^*$ and $G$ have resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

Using these ingredients, we obtain the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y$}%%  \textbf{Let}
\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|^2 < 1$; $k = 0$.\\
\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
\Repeat{
  convergence}{
  \begin{eqnarray*}
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma (e - E\tilde{x}^{(k)})\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
\label{Tab:pseudocode_pb}
\end{algorithm}

@@

\medskip \noindent
\textbf{Acknowledgments:}
This work was supported by the  Human Brain Project.

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
\end{document}
